Removing nonlinear batch effects using adversarial deep neural networks

### 2019-04-11 thesis.tex
Add a few points to discussion

\begin{enumerate}
	\item Nonlinear interactions still remain after ComBat for larger datasets
	\item Simple metrics aren't enough to identify the nonlinear interactions, but different classifiers help
	\item ComBat works really well for small, traditional datasets % include flip side for #s 3&4
	\item Confounded removes nonlinear effects in larger datasets
	\item Confounded shows promise for other confounders, not just batch effects (could work with combining rnaseq + microarray) and seems to work with multiple types of data
\end{enumerate}

>>>>

\begin{enumerate}
	\item Nonlinear interactions still remain after ComBat for larger datasets
	\begin{enumerate}
		\item Random Forests often has high batch classification accuracy after ComBat-adjustment.
	\end{enumerate}
	\item Simple metrics aren't enough to identify the nonlinear interactions, but different classifiers help
	\begin{enumerate}
		\item Figs \ref{fig:mmd} and \ref{fig:mse} both show that ComBat performed better than Confounded for the MNIST dataset, but the effects left after ComBat finished are still identifiable by Random Forests with 99.9\% accuracy (Table \ref{tab:batch}).
	\end{enumerate}
	\item ComBat works really well for small, traditional datasets % include flip side for #s 3&4
	\item Confounded removes nonlinear effects in larger datasets
	\item Confounded shows promise for other confounders, not just batch effects (could work with combining rnaseq + microarray) and seems to work with multiple types of data
\end{enumerate}
